MYC overrides HIF-1α to regulate proliferating primary cell metabolism in hypoxia

### 2023-04-20 manuscript/manuscript.qmd
add hypoxia plus BAY fluxes

>>>>

## Hypoxia prevents BAY from increasing glycolysis

To reconcile the differential effects of prolyl hydroxylase inhibition by hypoxia and BAY, we next addressed whether hypoxia could suppress the effects of BAY on glucose and lactate fluxes (**Figure 8**). LFs cultured in standard growth medium were treated with BAY and placed in either 21% or 0.5% oxygen. Similar to previous experiments, BAY treatment decreased cell growth rate, increased glucose uptake, and increased lactate efflux in 21% oxygen. However, when combined with 0.5% oxygen, BAY treatment was unable to enhance lactate efflux. These data demonstrate that hypoxia antagonizes the effects of HIF-1α activation on glycolytic flux in these cells.

We observed a similar pattern using RNA interference to silence PHD2 expression (**Figure 8 - figure supplement 1**).
